Manuscript title here

### 2022-01-14 doc/ms/ms.Rmd
introduction work and incorporating methods/results simplification

<!--- warming and effects in food webs --->
Temperature is an important abiotic variable with increasing relevance as warming global temperatures alter the diversity, structure, and functioning of Earth's ecosystems
[@walther2002]. The effects of temperature on ecosystems manifest through complex direct and indirect pathways such as shifting species ranges and subsequent changes to local and regional communities [@root2003], species adaptations [@gibert2017], and through effects on individual metabolic rates [@brown2004; @gillooly2001].

<!--- Speeding up of food web: Species levels--->
Temperature has the potential to alter the provision and maintenance of ecosystem services by modifying the network of interactions among species [@brose2012; @woodward2010] that underpin ecosystem functions [@deruiter1995; @thompson2012]. Across global climate gradients, temperature mediates the dynamics and stability of food webs [@baiser2019] by altering the acquisition and allocation of resources among species [@zhang2017] and ultimately the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019]. Importantly, these effects operate directly through temperature's influence on individual metabolic rates [@gillooly2001, @brown2004] and biological activity [e.g., attack rate, handling time, growth rates, etc.; @dell2014], and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017]...

<!--- Connect traits to the 'speed' of ecosystem energy fluxes--->

In fact, reduced organismal body size with warming is considered a 'universal' response of climate change....

Here, we measured the patterning and distribution of organic matter fluxes within invertebrate food webs across a natural stream temperature gradient (\~5--28$^\circ$C). Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
[@ogorman2012; @hood2018]. Consumers rely largely on autochthonous resources [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020]. As such, we predicted total annual OM fluxes to consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams. We further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities. The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size.

@@

We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N 021$^\circ$ 18'W) that varied in mean annual temperature. Hengill is
characterized by indirect geothermal heating of groundwater [@arnason1969], leading to a natural variability in water temperatures (4.5--54.0 $^\circ$C), but similar solute
chemistries [@friberg2009]. These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman2014; @nelson2017a]. We selected
streams to maximize the temperature range, while minimizing differences in the structural aspects of primary producers. In each stream, we measured temperature and water depth
every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp. Pocasset, MA, USA). Light availability in the watershed was measured every 15
min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp. Pocasset, MA, USA).

@@

We sampled macroinvertebrate communities approximately monthly from July 2011 to August 2012 in four streams and from October 2010 to October 2011 in two streams used in a previous
study (*n* = 6 streams). The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental
manipulation [@nelson2017; @nelson2017a]. Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in
unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018]. We collected fiver Surber samples
(0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream. Within the sampler, inorganic substrates were disturbed to \~10 cm depth and invertebrates and
organic matter were removed from stones with a brush. Samples were then preserved with 5% formaldehyde until laboratory analysis. In the laboratory, we split samples into coarse
(\>1 mm) and fine (\<1 mm but \>250 $\mu$m) fractions using nested sieves and then removed invertebrates form each fraction under a dissecting microscope (10--15 x magnification).
For particularly large samples, fine fractions were sub-sampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates. Subsamples were scaled to
the rest of the sample assuming similar abundance and body size distributions. Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with
taxonomic keys [@peterson1977; @merritt2008; @andersen2013]. Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.

@@

**Come back and confirm this section** Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
= 3--5) to ensure samples contained enough material for quantification. We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut content
slides. Briefly, we removed the foregut from each individual or collection of individuals and sonicated gut contents in water for 30 seconds. Gut content slurries were filtered
onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a
microscope slide, cleared with Type B immersion old, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
using image analysis software [@schindelin2012]. We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
plants (e.g., bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.

To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, in stream, *j*, is a multinomial vector,$\overrightarrow{y_{ij}}$, of
$$\overrightarrow{y_{ij}} \sim Multinomial(\overrightarrow{p_{ij}}, n_{ij})$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value. **add in
site-level model parameter and model fitting language** . Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing
values.

@@

```
## Community OM fluxes

@@

@@

>>>>

<!--- warming and effects in food webs --->
<!--- Speeding up of food web: Species levels--->
Increasing global temperatures are altering the provisioning and maintenance of ecosystem services by modifying the network of interactions among species that underpin ecosystem functions [@brose2012; @woodward2010; @deruiter1995; @thompson2012]. Across global climate gradients, temperature mediates the dynamics and stability of food webs [@baiser2019] by altering the acquisition and allocation of resources among species [@zhang2017] and ultimately the magnitudes and relative distribution of biomass and interactions among species and trophic levels [@may1972; @mccann1998; @barnes2018; @gibert2019]. Temperature's effects permeate across levels of biological organization from its control on individual metabolic rates [@gillooly2001, @brown2004] and biological activity [e.g., attack rate, handling time, growth rates, etc.; @dell2014], as an environmental niche filter of community assembly [] and indirectly through the distribution of species traits, such as body size, within and across species [@bideault2019; @nelson2017].

<!--- Connect traits to the 'speed' of ecosystem energy fluxes--->
In fact, reduced organismal body size with warming is considered a 'universal' response to climate change [@atkinson1994; @daufresne2009]. Body size reductions arise from multiple mechanisms acting at different levels of organization, such as the increased relative abundance of smaller species within warmer communities [@bergmann1848], or smaller individuals in warmer populations [@james1970], or lastly through reduced body size of warmer individuals [@atkinson1994]. Temperature-size relationships (TSR) are likely to influence the distribution of body sizes both across and within ecosystems, such that warmer communities should contain smaller species and populations, on average, and smaller organisms should be more dominant within a community. These changes can have important implications for ecosystems pattern and processes because body size is a strong determinant of organismal biology [@peters1983], influencing life history [@zuess2017; @altermatt2010] and development [@angilleta], diet breadth [], trophic position [], and crucially, metabolic rate [@brown2004].

Organismal metabolic rate, in addition to being controlled by body size, is strongly influenced by  temperature [@gilooly2001; @arrhenius1898]. Therefore, temperature may alter metabolic rate indirectly through reductions in body size, as well as directly through its effects on subcellular kinetics [@bideault2019]. The interactive effect of these processes has been shown to modulate ecosystem patterns through effects on population abundance [@bernhardt2019], consumer-resource interactions [@bideault20149], and food web structure [@gibert2019]. Importantly, the kinetic effects of temperatures are tied to many biological processes [@dell2014], among them growth rate [@giloolly2001`], developmental rate [@zuo2012], and population turnover rate [@]. As such, the emerging picture suggests a smaller, faster world in which warming can "speeds up" ecosystem processes through the compounded effects of smaller body size and higher biological rates.

Yet, considerable uncertainty remains in the predicted short- and long-term effects of climate warming, especially at higher levels of organization such as communities and food webs *more*[@woodward2010; @walther2005]. For example, we lack a complete understanding of TSRs to explain deviations that exist across taxonomic groups [e.g., diatoms, @adams2013; invertebrates @zeuss2017; birds @geist1987; and fish @rypel2014]. Explanations for these deviations vary [@ohlberger2013], some highlight additional processes such as competition [] and predation [@delong2014], while others propose alternative models of organism body size optimization, such as the balance of resource supply and energy demand [e.g., @kozlowski2004; @delong2012]. Crucially, these alternative models highlight the trade-off between asymptotic body size and metabolic demand [@delong2012] that can shape life history patterns [i.e., voltinism, @zuess2017].  and community structure across ecosystems...*better transition here maybe*

These maxmize energy intake when resources are available [@atkinson1997]

- Seasonal systems have unique constraints
- These seasonal constraints are greater at higher temps
- This creates a situation where body sizes are selected for that 1) stabilize c-r dynamics [@osmond2017],
2) availability

Here, we measured the patterning and distribution of energy fluxes within invertebrate food webs across a natural stream temperature gradient (\~5--28$^\circ$C). Previous research in these streams has shown a strong positive effect of temperature on primary production both among streams [@demars2011; @padfield2017] and within streams seasonally
[@ogorman2012; @hood2018]. Consumers rely largely on autochthonous resources [@ogorman2012; @nelson2020] and therefore the dynamics of primary production have a strong control on consumer energy demand [@junker2020]. As such, we predicted annual energy fluxes of consumers to scale with among-stream patterns in resource availability and consumer energy demand and increase with temperature across streams. We hypothesized temperature to be a strong environmental filter of community assembly and energy flux, especially at the extremes. From this we propose a number of predictions regarding the patterning of energy fluxes within and across communities of different temperature, with particular focus on two species traits: body size and population biomass turnover (production:biomass ratios, *P:B*). First, we predict warmer temperatures should select for smaller and faster turnover species leading to a decrease in body sizes and increase in *P:B* on average across communities. Second, within communities energy fluxes should be dominated by smaller, higher turnover species at warmer temperatures. Third,

e further expected that increasing temperature would reduce consumer species richness [@ogorman2019], thereby altering how OM fluxes are distributed within and across communities. We predicted OM fluxes would be most even at moderate temperatures and dominated by few taxa at the coldest and warmest extremes. Lastly, we predicted that temperature is a strong filter of community assembly  Lastly, we quantified how OM fluxes were associated with two key species traits; body size and population production to biomass ratio (P:B) within communities. We predicted mean community body size would decrease and mean community P:B ratios would increase at higher temperatures. The distribution of OM fluxes to consumers will shift towards relatively faster, higher turnover consumer at higher temperatures, 'speeding up' consumer dynamics both through direct effects on consumer turnover and through a decrease in mean body size.

@@

We studied six streams within the Hengill geothermal field of southwestern Iceland (64$^\circ$ 03'N 021$^\circ$ 18'W) that varied in mean annual temperature. Hengill is
characterized by indirect geothermal heating of groundwater [@arnason1969], leading to natural variability in water temperatures (4.5--54.0 $^\circ$C), but similar solute
chemistries [@friberg2009]. These conditions create a "natural laboratory" for isolating the effects of temperature on ecosystem processes [@ogorman2014; @nelson2017a]. We selected
streams to maximize the temperature range, while minimizing differences in the structural aspects of primary producers. In each stream, we measured temperature and water depth
every 15 min from July 2010 through August 2012 (U20-001-01 water-level logger, Onset Computer Corp. Pocasset, MA, USA). Light availability in the watershed was measured every 15
min from atmospheric stations (HOBO pendant temperature/light UA-002-64, Onset Computer Corp. Pocasset, MA, USA).

@@

We sampled macroinvertebrate communities approximately monthly from July 2011 to August 2012 in four streams and from October 2010 to October 2011 in two streams used in a previous
study (*n* = 6 streams). The two streams were part of an experiment beginning October 2011, therefore overlapping years were not used to exclude the impact of experimental
manipulation [@nelson2017; @nelson2017a]. Inter-annual comparisons of primary and secondary production in previous studies showed minimal differences among years in
unmanipulated streams, suggesting that combining data from different years would not significantly bias our results [@nelson2017; @hood2018]. We collected five Surber samples
(0.023 m^2^, 250 $\mu$m mesh) from randomly selected locations within each stream. Within the sampler, inorganic substrates were disturbed to \~10 cm depth and invertebrates and
organic matter were removed from stones with a brush. Samples were then preserved with 5% formaldehyde until laboratory analysis. In the laboratory, we split samples into coarse
(\>1 mm) and fine (\<1 mm but \>250 $\mu$m) fractions using nested sieves and then removed invertebrates from each fraction under a dissecting microscope (10--15 x magnification).
For particularly large samples, fine fractions were sub-sampled (1/2--1/16th) using a modified Folsom plankton splitter prior to removal of invertebrates. Subsamples were scaled to
the rest of the sample assuming similar abundance and body size distributions. Macroinvertebrates were identified to the lowest practical taxonomic level (usually genus) with
taxonomic keys [@peterson1977; @merritt2008; @andersen2013]. Taxon-specific abundance and biomass were scaled to a per meter basis by dividing by the Surber sampler area.

@@

Macroinvertebrate diets were quantified for dominant taxa in each stream. We focused on numerically abundant taxa and/or taxa with relatively
high annual production. A minimum of five individuals were selected from samples, and, when possible included individuals of different size classes to account for ontogenetic
shifts in diet. We included individuals from different seasons to capture concurrent ontogenetic and seasonal changes. For small-bodied taxa, we combined multiple individuals (*n*
= 3--5) to ensure samples contained enough material for quantification. We used methods outlined in Rosi-Marshall [-@rosi-marshall2016] to remove gut tracts and prepare gut contents for quantification. Briefly, we removed the foregut from each individual or collection of individuals and sonicated contents in water for 30 seconds. Gut content slurries were filtered
onto gridded nitrocellulose membrane filters (Metricel GN-6, 25 mm, 0.45 $\mu$m pore size; Gelman Sciences, Ann Arbor, MI, USA), dried at 60 $^\circ$C for 15 min, placed on a
microscope slide, cleared with Type B immersion oil, and covered with a cover slip. We took 5--10 random photographs under 200--400x magnification, depending on the density of
particles, using a digital camera mounted on a compound microscope. From these photographs we identified all particles within each field and measured the relative area of particles
using image analysis software [@schindelin2012]. We identified particles as diatoms, green and filamentous algae, cyanobacteria, amorphous detritus, vascular and non-vascular
plants (e.g., bryophytes), and animal material. We calculated the proportion of each food category in the gut by dividing their summed area by the total area of all particles. Gut
contents of many predators were empty or contained unidentifiable, macerated prey. For these taxa, we assumed 100% animal material.

To estimate variability in diet compositions and to impute missing values for non-dominant, yet present, taxa, we modeled the diet proportions within each stream using a
hierarchical multivariate model [@fordyce2011, @coblentz2017]. Here, the diet of a consumer population, *i*, in stream, *j*, is a multinomial vector,$\overrightarrow{y_{ij}}$, of
$$\overrightarrow{y_{ij}} \sim Multinomial(\overrightarrow{p_{ij}}, n_{ij})$$ $$\overrightarrow{p_i} \sim Dirichlet(\overrightarrow{q_i} \times  \alpha) $$ where, $\overrightarrow{p_i}$, is
a vector of consumer diet proportions, $\overrightarrow{q_i}$ is a vector of the population's diet proportions and $\alpha$ is a concentration parameter of the Dirichlet process.
We used uniform priors for $\overrightarrow{q_i}$ and $\alpha$, $$\overrightarrow{q_i} \sim Dirichlet(\overrightarrow{\textbf{1}})$$ $$\alpha \sim Uniform(0,\textit{c})$$ where,
$\overrightarrow{\textbf{1}}$ is a vector of ones the same length of basal resource types and $\textit{c}$ is the presumed maximum value the concentration value. Models were fit in Stan with the 'brms' package in R [@burkner2017]. For non-dominant taxa, diet proportions were imputed
from the hierarchical model by resampling from posterior distributions. Importantly, this process allowed to maintain the hierarchical structure of the data when imputing missing values.

@@

drake::loadd(temperature_stats)

## Community OM fluxes

@@

General patterns of community change and species identity across the gradient.
Community and population patterns of M and P:B with temperature...

@@

**I am strongly considering ditching or appendixing the diet stuff. This will become important for the next paper, however, I think it distracts from the story here since we are really just focused on the energy pathways**
